Analysis and approximation of mixed-dimensional PDEs on 3D-1D domains coupled with Lagrange multipliers

### 2020-09-22 reply_to_reviewers.tex

\documentclass{article}
\usepackage{fullpage}
\newenvironment{answer}{\begin{paragraph}{Answer:}}{\end{paragraph}\vspace{0.5cm}}
\usepackage{xcolor}

\newcommand{\fede}[1]{{\color{green!55!blue}#1}}
\newcommand{\kent}[1]{{\color{red}#1}}
\newcommand{\miro}[1]{{\color{blue}#1}}
\newcommand{\paolo}[1]{{\color{magenta}#1}}

@@

\vspace{1cm}

\section*{Reviewer \#1}

In the paper under review the authors study an example of mixed dimensional PDE, i.e. a 3D problem coupled with a 1D problem. Such problems naturally appear in various applications (e.g. biomedicine and geophysics) where slender cylindrical structures are coupled with larger 3D body. The main issue in the analysis of such problem is that trace is not well defined on set of co-dimension two for weak solutions. The authors circumvent this issue by exploiting the fact that the thin structure is not 1D curve, but rather a slender 3D structure. This leads to two formulation of the problems: 3D-1D-1D and 3D-1D-2D. The former is obtained from the latter by averaging procedure. Neumann (dynamic) coupling conditions are enforced by using a Lagrange multiplier. Well-posednes is proved for the continuous and the discrete version of the problem. Two different version of the discrete case are analyzed: the case when 3D and 1D mesh matches on the interface (the conforming case) and the case when the meshes do not necessarily match (the non-conforming case). Since the saddle point approach is used, the main technical step is to prove that inf-sup condition is satisfied. In the non-conforming case the stabilization operator is constructed in order to satisfy inf-sup condition. Finally, the comparison of the numerical solution with analytical solution for benchmark problem is presented.

The result presented in the paper are interesting and to the best of my knowledge correct. I recommend the paper for publication in the SINUM.
Remarks:
\begin{enumerate}
    \item Please explain what is unknown $\lambda$ in problem (1.1). I suggest including part of the Appendix from supplementary materials where $\lambda$ is introduces as a Langrange multiplier.
    \item Sectio 2, page 2 - $\Omega$ is open? Maybe replace "in detail" with "More precisely".\\
    \fede{The standard definition of domain is used, i.e. $\Omega$ is a open and connected set. For clarity, the definition has been added to the manuscript. }
    \item P. 3. - Please provide references for $H^{1/2}_{00}$ and interpolation of weighted spaces. In addition, it would be instructive to provide an example for Riesz map S.
    \item p.4. (l145-l50) I suggest rewriting this paragraph. First, please refer to the exact result that you are using (from [22] or [28]) and define or refer to definition of "domains having small geometric details". Second, it is not necessary to define operator norm, but enough to say that norm of $H_{\Omega}$ is uniformly bounded.\\
    \fede{We thank the reviewer for the suggestion. In the revised manuscript, the extension operator has been replaced by the harmonic extension, therefore the reference to [28] is not needed.\\
    WHAT DOES THE SECOND PART MEAN? }
    \item p4 l152. Is $H_{\Omega}$ harmonic extension? If so, please state this in previous paragraph.\\
    \fede{Yes, the definition has been added in the revised manuscript.}
    \item p8 l177-l184 - I suggest adding a figure that illustrate the assumptions on the conforming mesh.
    \item p9 (4.4) Reference for these properties of $SZ_h$\\
    \fede{The reference has been added in the revised manuscript.\\

    CHECK: LEMMA 1.130 FROM ERN AND GUERMOND. (4.4) IS OBTAINED FROM (i) WITH l=1, p=2, m=1. (4.5) IS OBTAINED FROM (ii) WITH l=1, p=2, m=0}
    \item p9, after (4.5) Do you mean inverse Poincare inequality?\\
    \fede{Yes it is a discrete inverse Poincare inequality. We adopt the terminology used in [Ern and Guermond, Ch. 1.7] where these inequalities are more in general addressed as inverse inequalities. }
    \item In statement of problem (5.1) include $\lambda$ and then say that one can construct explicit solution with $\lambda=0$.\\
    \fede{The entire paragraph has been revised. Notice that $\lambda$ cannot be included in problem (5.1) because (5.1) is not the strong formulation of problems (2.2) and (2.4). It is only an auxiliary problem used to fabricate the weak solution of problems (2.2) and (2.4).}
\end{enumerate}
